Trial by Fire: Diachronic and Regional Sentiment Towards American Wildfires

### 2022-12-12 paper.Rmd
Updated References

To overcome this issue, we decided to use Cardiff's roBERTa-base model for sentiment analysis as well.^[https://huggingface.co/cardiffnlp/twitter-roBERTa-sentiment-latest] This model was trained on roughly 124 million tweets from January 2018 to December 2021, using the TweetEval benchmark to fine tune the sentiment analysis. The model outputs probabilities that a tweet is positive, neutral, or negative. For the purposes of our analysis, we simplified the output to a categorical variable representing the sentiment with the highest probability. (Strength of sentiment was not captured.)

@@

>>>>

To overcome this issue, we decided to use Cardiff's roBERTa-base model for sentiment analysis as well.^[https://huggingface.co/cardiffnlp/twitter-roberta-base-sentiment-latest] This model was trained on roughly 124 million tweets from January 2018 to December 2021, using the TweetEval benchmark to fine tune the sentiment analysis. The model outputs probabilities that a tweet is positive, neutral, or negative. For the purposes of our analysis, we simplified the output to a categorical variable representing the sentiment with the highest probability. (Strength of sentiment was not captured.)

@@

## References

Anon. n.d. “Wildfires and Acres.” Nifc.gov. \
(https://www.nifc.gov/fire-information/statistics/wildfires)

Jockers, M. (2020), “Syuzhet Package - RDocumentation.” Rdocumentation.org. \
(https://www.rdocumentation.org/packages/syuzhet/versions/1.0.6).

Lou, D & Camacho-Collados, J (2022).
“Cardiffnlp/Twitter-Roberta-Base-Sentiment-Latest · Hugging Face.” 
Huggingface.Co. \
(https://huggingface.co/cardiffnlp/twitter-roberta-base-sentiment-latest).

Sagar, Chaitanya. 2018. “Twitter Sentiment Analysis Using R.” Dataaspirant. \ 
(https://dataaspirant.com/twitter-sentiment-analysis-using-r/).

### Please see submitted GitHub Repository for associated Code Appendix
